---
title: "RFID Lab Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: yeti
    social: [ "twitter", "facebook", "menu"]

  knit: (function(input_file, encoding) {
      out_dir <- 'docs';
      rmarkdown::render(input_file,
      encoding=encoding,
      output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
```

```{r}
data <- read.csv("ThesisDataset.csv")
```

```{r}
mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")
```



Dashboard
=====================================

Column {data-width=225}
-------------------------------------

### Total Students

```{r}
valueBox(length(data$ï..Student.Name),
         color = "orange")
```

### Report Submitted

```{r}
valueBox(sum(data$Report.Submitted == "Yes"), color = "skyblue")
```

### Experiment Successful

```{r}
valueBox(sum(data$Result.of.Experiment == "Success"),
         color = "lightgreen")
```


Column {data-width=350}
-----------------------------------------------------------------------

### Experiment Time Analysis

```{r}
p1 <- data %>%
         group_by(ï..Student.Name) %>%
         plot_ly(x = ~ï..Student.Name,
                 y = ~Time.taken.for.experiment,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Students"),
yaxis = list(title = 'Time (hrs)'))
p1
```

### Quiz Result Analysis

```{r}
p2 <- data %>%
         group_by(Quiz.result) %>%
         summarise(count = n()) %>%
         plot_ly(labels = ~Quiz.result,
                 values = ~count,
                 marker = list(colors = mycolors)) %>%
         add_pie(hole = 0.2) %>%
         layout(xaxis = list(zeroline = F,
                             showline = F,
                             showticklabels = F,
                             showgrid = F),
                yaxis = list(zeroline = F,
                             showline = F,
                             showticklabels=F,
                             showgrid=F))
p2
```


Column {data-width=350}
-----------------------------------------------------------------------

### Forum Interaction Analysis

```{r}
p3 <- plot_ly(data, x=~Question.Asked) %>%
         add_markers(y = ~Question.Answered,
                     text = ~paste("Question Answered in forum: ", Question.Answered),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(Question.Answered ~ Question.Asked)),
                   name = "Loess Smoother",
                   color = I("#FFC125"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "Question Asked"),
                yaxis = list(title = "Question Answered"))
p3
```

### Quiz Time Analysis

```{r}
p4 <- plot_ly(data, x = ~ï..Student.Name, y = ~Time.taken.for.Quiz, type = 'scatter') %>%
         layout(xaxis = list(title = "Student"),
                yaxis = list(title = "Quiz Time"))
p4

```


Experiment Data
=========================================

### In Depth View of the Method Used in Experiment

```{r}
p5 <- plot_ly(data, x = ~ï..Student.Name, y = ~Transponder.Selected, text = ~Substrate.Selected, type = 'scatter', mode ='markers',
        marker = list(size = ~Time.taken.for.experiment*5, opacity = 1))%>% layout(
         xaxis = list(title = "Name of student"),
         yaxis = list(title = "Transponder selected"))

p5

```


Lab Data
========================================

```{r}

datatable(data,
          colnames = c('Student Name', 'Downloaded Experiment Guide', 'Result of Experiment', 'Time taken for experiment', 'Report Submitted', 'Question Asked', 'Question Answered', 'Quiz result', 'Time taken for Quiz', 'Method seleted', 'Substrate Selected', 'Transponder Selected'),
          caption = "RFID Lab Interaction Data",
          rownames = T,
          filter = "top",
          style = 'bootstrap4',
          options = list(pageLength = 25))
```


About Dashboard
========================================

Created by: Prantik Chatterjee

This dashboard is developed as a part of submission of my Masters Thesis on Learning Analytics Concept for learning RFID Basics in a Lab. The report of this thesis work is submitted along with this dashboard.

Data used: Dummy data is generated. Any resemblance to reality is pure coincidence. 

